% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Shuyuan Zhao}
\contactInfo{(+86) 185-1860-8351}{shuyuan.zhao@hotmail.com}{}{}
 
\section{PROFILE}
Diven Data Engineer with 4+ years background in designing and developing Business Intelligence applications.
Experience with distributed systems operating in a scalable/high volume environment.
Adept at problem solving, critical thinking and proven coding ability with proficiency in Java, Python, SQL, Spark, ClickHouse.
Passionate about using data to improve the world around us and building products with great business impact.

\section{SKILLS}
\begin{itemize}[parsep=0.2ex]
  \item \textbf{Programming}: Java, Python, Scala, SQL
  \item \textbf{Big data}: Spark, ClickHouse, Yarn, Hive, OLTP/OLAP
  \item \textbf{Middleware}: Redis, Elasticsearch, Zookeeper, Thrift, Massage Queue
\end{itemize}

\section{WORK HISTORY}
\datedsubsection{\textbf{ByteDance | Big Data Engineer}, Beijing}{2019.12 - Currenct}
\begin{itemize}
  \item Responsible for architecture design and implementation of the next generation BI tools 
  which help advertisers gain business insights and power their long-term success.
  \item Own projects and responsible for the full software development life cycle 
  including requirements collection, technical designs, implementation, testing and operations.
  \item Build robust and scalable distributed systems and data integration pipelines 
  using SQL, JAVA, Spark, ClickHouse for real-time analytics and offline data processing. 
  \item Create complex SQL queries utilizing best query-writing practices.
  \item Develop the back end of websites, build databases such as MySQL, ES, Abase(RocksDB), and provide APIs for internal and external used.
  \item Collaborate with product managers and other technical teams in designing and deploying competitive marketing initiatives and impactful digital strategies.
  \item Conduct researches and deep dive into ad-hoc issues with fast action for troubleshooting and effective presentation for customer consulting.
  
\end{itemize}

\datedsubsection{\textbf{Iconma | Data Analyst}, Richmond, VA, US}{2018.2 - 2019.11}
\begin{itemize}
  \item Worked at the brand and marketing credit card department in Capital One Bank.
  \item Performed segmentation analytics for marketing campaigns and customer management with SQL and BI tools.
  \item Conducted A/B testing on business strategies and analyzed their performance.
\end{itemize}

\section{PROJECTS}
\datedsubsection{\textbf{Advertising Effectiveness Measurement}}{ByteDance}
\begin{itemize}
  \item Provided detailed overview of campaign performance and determined the true effectiveness of marketing strategies by analyzing impressions, engagement, ads placements, ROI, online-to-offline sales impact.
  \item Developed scalable and fault tolerance Spark applications based on Spring framework for data transformations and data analysis.
  \item Designed and developed data processing pipelines which involved in data loading, writing Hive UDFs and conducting operative practices on Spark performance tuning.
\end{itemize}

\datedsubsection{\textbf{Audience Segmentation and CRM tools}}{ByteDance}
\begin{itemize}
  \item Created audience segmentation and built customer relationship management(CRM) system to organize and make sense of valuable audience data and insights.
  \item Performed real-time analytics for audience size estimation, audience profiling, drill down analysis with ClickHouse MergeTree engine and processed petabytes of data within seconds.
\end{itemize}

\section{EDUCATION}
\datedsubsection{\textbf{The George Washington University}, Data Science,\textit{ Master of Science}}{2015.8 - 2017.5}
\datedsubsection{\textbf{Central South University(中南大学)}, Statistics,\textit{ Bachelor of Science}}{2011.9 - 2015.6}

\end{document}
